---
title: "LinkPrediction"
author: "Zahra Khoshmanesh"
date: "5/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(linkprediction)
library(igraph)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(lattice)
library(caret)
library(C50)
library(kernlab)
library(mlbench)
library(randomForest)
library(caretEnsemble)
library(MASS)
library(klaR)
library(nnet)
```

## Rq3: What similarity metrics do perform better in the context of feature interaction detection?


### creating Email graph

```{r}
#creating graph of interactions
el_name <-  matrix(c("Decrypt","Forward",
                       "AddressBook","Encrypt",
                       "Sign","Verify",
                       "Sign","Forward",
                       "Encrypt","Decrypt",
                       "Encrypt","Verify",
                       "Encrypt","AutoRespond",
                       "Encrypt","Forward",
                       "Decrypt","AutoRespond",
                       "Verify","Forward"), nrow = 10, ncol = 2, byrow = TRUE)

interaction_graph <- graph_from_edgelist(el_name,directed = FALSE)
interaction_graph

plot(interaction_graph, layout=layout_with_graphopt, vertex.color="lightgreen",edge.color="red",vertex.shapes="circle",vertex.size=30,edge.size=45)



```

## create unwanted feature interaction matrix of the Email Software Product Line

Decrypt: 1
Forward: 2
AddressBook: 3
Encrypt: 4
Sign: 5
Verify: 6
AutoRespond: 7


```{r}

#create unwanted feature interaction matrix of email system

        fi <- matrix(c(1,2,
                       3,4,
                       5,6,
                       2,5,
                       1,4,
                       4,6,
                       4,7,
                       2,4,
                       1,7,
                       2,6,
                       1,3,#non fi nodes starts here
                       1,5,
                       1,6,
                       2,3,
                       2,7,
                       3,5,
                       3,6,
                       3,7,
                       4,5,
                       5,7,
                       6,7
                       ), nrow = 21, ncol = 2, byrow = TRUE)

#print and check the graph

fi 

```


```{r}
#create graph out of unwanted feature interaction matrix for email, the matrix is undirected
g <- graph_from_edgelist(fi,directed = FALSE)
#check the output of graph
g


```


```{r}

#fi attributes shows which eges contributes to feature interactions

g <-set.edge.attribute(g, "fi", value=c("TRUE", "TRUE","TRUE","TRUE","TRUE","TRUE", "TRUE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("FALSE", "TRUE","TRUE","TRUE","TRUE","TRUE", "TRUE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

#set p2 as unwanted feature interactions exists in version 2 of the email product line 
g <-set.edge.attribute(g, "p2", value=c("TRUE", "TRUE","TRUE","TRUE","TRUE","TRUE", "TRUE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "fi")

get.edge.attribute(g, "p1")

get.edge.attribute(g, "p2")

```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```

### Similarity metrics:

local
global

```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

### create the test set: version 2 of email that has all unwanted feature interactions 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
    vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```

## Unwanted Feature Interaction (1th) : 


```{r}



#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("FALSE", "TRUE","TRUE","TRUE","TRUE","TRUE", "TRUE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "p1")



```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```


```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
  vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```



## Unwanted Feature Interaction (2nd) :


```{r}



#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("TRUE", "FALSE","TRUE","TRUE","TRUE","TRUE", "TRUE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "p1")



```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```


```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
  vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```


## Unwanted Feature Interaction (3rd) : 


```{r}



#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("TRUE", "TRUE","FALSE","TRUE","TRUE","TRUE", "TRUE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "p1")



```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```


```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
  vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```


## Unwanted Feature Interaction (4th) :


```{r}



#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("TRUE", "TRUE","TRUE","FALSE","TRUE","TRUE", "TRUE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "p1")



```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```


```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
  vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```



## Unwanted Feature Interaction (5th) : ()


```{r}



#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("TRUE", "TRUE","TRUE","TRUE","FALSE","TRUE", "TRUE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "p1")



```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```


```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
  vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```


## Unwanted Feature Interaction (6th) : ()


```{r}



#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("TRUE", "TRUE","TRUE","TRUE","TRUE","FALSE", "TRUE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "p1")



```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```


```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
  vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```


## Unwanted Feature Interaction (7th) : ()


```{r}



#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("TRUE", "TRUE","TRUE","TRUE","TRUE","TRUE", "FALSE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "p1")



```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```


```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
  vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```


## Unwanted Feature Interaction (8th) : ()


```{r}



#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("TRUE", "TRUE","TRUE","TRUE","TRUE","TRUE", "TRUE","FALSE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "p1")



```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```


```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
  vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```


## Unwanted Feature Interaction (9th) : ()


```{r}



#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("TRUE", "TRUE","TRUE","TRUE","TRUE","TRUE", "TRUE","TRUE","FALSE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "p1")



```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```


```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
  vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```


## Unwanted Feature Interaction (10th) : ()


```{r}



#set p1 as unwanted feature interactions exists in version 1 of the email product line, 
g <-set.edge.attribute(g, "p1",  value=c("TRUE", "TRUE","TRUE","TRUE","TRUE","TRUE", "TRUE","TRUE","TRUE","FALSE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))

get.edge.attribute(g, "p1")



```

```{r}
# set train as edges contribute to  unwanted feature interactions in version 1 of email product line ("forward" is not in version 1)
train <- delete.edges(g, which(E(g)$p1==FALSE))

train
 
```


```{r}
#add similarity metrics to training data

  #local similarity metrics

  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)



```

 

```{r}

#"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)


testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )

testdf

testdf %>%
 count(p1, p2, test)

```

```{r}

testdf <- testdf %>%
 filter(p1==FALSE)

testdf

 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
   
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )

preds

```

```{r}
library(ROCR, warn.conflicts = FALSE)
#preds <- preds %>% mutate(test=ifelse(to %% 2==0,TRUE,FALSE))

predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )

names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")

perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  )
  }
  
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  

  
```

```{r}
  vapply(
  predlist,
  function(p) performance(p, "auc")@y.values[[1]],  numeric(1)
  )
```


```{r}

FI_detection <- function(g){
  
  ####################################################
  train <- delete.edges(g, which(E(g)$p1==FALSE))
  ####################################################
  aa <- proxfun(train, method="aa", value="edgelist") %>% dplyr::filter(from < to) %>% dplyr::rename(aa=value)
  
  #pa <- proxfun(train, method="pa", value="edgelist") %>%  filter(from < to) %>%  rename(pa=value)
  
  cosi <- proxfun(train, method="cos_l", value="edgelist") %>% dplyr:: filter(from < to) %>% dplyr::rename(cosi=value)
  
  cn <- proxfun(train, method="cn", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(cn=value)
  
  jaccard <- proxfun(train, method="jaccard", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr::rename(jaccard=value)
  
  ra <- proxfun(train, method="ra", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(ra=value)
  
  #global similarity metrics
  
  katz <- proxfun(train, method="katz", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(katz=value)
  
  #act <- proxfun(train, method="act", value="edgelist") %>%  filter(from < to) %>%  rename(act=value)
  
  lp <- proxfun(train, method="lp", value="edgelist") %>%  dplyr::filter(from < to) %>% dplyr:: rename(lp=value) 
  
  rwr <- proxfun(train, method="rwr", value="edgelist") %>%  dplyr::filter(from < to) %>%  dplyr::rename(rwr=value)

  ##################################################
  
  #"true" edges from period 2
p2g<- igraph::as_data_frame(g, what="edges") %>% dplyr::as_tibble() %>% dplyr::filter(p2==TRUE)
##################################################

testdf <- tidyr::crossing(
  # All dyads -- all pairs of vertex ids
  from = seq(1, vcount(train)),
  to = seq(1, vcount(train))
  ) %>%
  # The network is undirected thus we keep
  # only unique unordered pairs of vertex ids
    dplyr::filter(from < to) %>%
  # Join "true" edges from period 2
  dplyr::left_join(p2g,  by = c("from", "to")  ) %>%
  # Dyads without a match (have NAs) are disconnected
  # so we convert NAs to FALSE
  mutate_at(
  c("fi","p1", "p2"),
  function(x) ifelse(is.na(x), FALSE, x)
  ) %>%
  # Create logical variable `test` to flag new co-authorships.
  # These are present in `p2` but absent in `p1`.
  mutate(
  test = (p2==TRUE & p1==FALSE)# new co-authorships
  )
  #######################################################
  testdf <- testdf %>% filter(p1==FALSE)
  ########################################################
 preds <- testdf %>%
   left_join(aa, by=c("from", "to")) %>%
   #left_join(pa, by=c("from", "to")) %>%
   left_join(cosi, by=c("from", "to")) %>%
   left_join(cn, by=c("from", "to")) %>%
   left_join(jaccard, by=c("from", "to")) %>%
   left_join(ra, by=c("from", "to")) %>%
   left_join(katz, by=c("from", "to")) %>%
   #left_join(act, by=c("from", "to")) %>%
   left_join(lp, by=c("from", "to")) %>%
   left_join(rwr, by=c("from", "to")) %>%
  mutate_at(
  c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr"), funs(ifelse(is.na(.), 0, .))
  )
  
  ##########################################################
  library(ROCR, warn.conflicts = FALSE)
  predlist <- lapply(
  c("aa","cosi","cn","jaccard","ra","katz","lp","rwr"),
  function(n) prediction(preds[[n]], preds$test)
  )
  names(predlist) <- c("aa", "cosi","cn","jaccard","ra","katz","lp","rwr")
  perflist <- lapply(predlist, performance, "tpr", "fpr")


  pal <- RColorBrewer::brewer.pal(8, "Set1")
  for(i in seq(along=perflist)) {
  plot(
  perflist[[i]],
  col = pal[i],
  add = i != 1
  ) }
  abline(a=0, b=1, lty="dashed")
  legend(
  "bottomright",
  title = "Methods",
  legend = c("Adamic-Adar", "Cosine based L+","Common Neighbour","Jaccard","RA","katz","lp","rwr"),
  lty = 1,
  col = pal,
  bty = "n"
  )
  
  ##########################################
  vapply( predlist,function(p) performance(p, "auc")@y.values[[1]],  numeric(1) )
  
}

```

### Detection of Uuwanted Feature Interaction ID=0

```{r}

g <-set.edge.attribute(g, "p1",  value=c("FALSE", "TRUE","TRUE","TRUE","TRUE","TRUE", "TRUE","TRUE","TRUE","TRUE",
                                        "FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE","FALSE"))
FI_detection(g)

```


